%==============================================================================
%  Chapter 1 — Introduction
%
%  Aims of this chapter (from the standard "research thesis" template):
%   1. Set the empirical and policy context.
%   2. Identify the gap / puzzle.
%   3. State the research question(s) and sub-questions.
%   4. Sketch the theoretical framing.
%   5. Outline the methodological approach.
%   6. Summarise contributions.
%   7. Map the rest of the thesis.
%==============================================================================
\chapter{Introduction}
\label{ch:introduction}

% ----------------------------------------------------------------------------
\section{Background and motivation}
\label{sec:intro-background}

The European Union's economic landscape is increasingly defined by a
\enquote{productivity gap} rooted in a structural failure to scale
deep-tech innovations. While the US and China have created dynamic
ecosystems that facilitate high firm turnover and the rise of new
industrial leaders, the EU's corporate landscape remains dominated by
established incumbents.

In response, the Union has moved beyond traditional market-failure
corrections, launching a series of high-stakes initiatives designed to
reform its industrial policy. These include the European Innovation
Council (EIC), the STEP Scale Up instrument, and the European Chips Act.
These are not mere funding programmes; they are strategic attempts to
foster both incremental growth in new and mature sectors and radical
breakthroughs in frontier technologies. However, this \enquote{reformist
turn} faces a fundamental paradox: the EU is attempting to catalyse
radical, high-uncertainty growth on a mandate built around market
stability, regulatory neutrality, and regional redistribution.

\todoinline{Tighten the two paragraphs above, anchor the productivity-gap
claim in 2--3 references (Draghi 2024; Letta 2024; JRC), and end with a
hand-off sentence: \enquote{This thesis interrogates how that paradox
is institutionalised inside two of the EU's most prominent reformist
instruments --- Pathfinder and STEP Scale Up.}}

% ----------------------------------------------------------------------------
\section{Problem statement and research gap}
\label{sec:intro-problem}
\todoinline{Articulate the empirical puzzle (Pathfinder and STEP coexist
inside the EIC Work Programme but appear to operate under different
investment logics --- exploratory grants vs.\ equity-based catalytic
investment) and the theoretical gap (institutional theory has
surprisingly little to say about supranational public investment
vehicles, particularly hybrid grant/equity instruments in the
mission-oriented mould). Anchor the gap in 3--5 references.}

% ----------------------------------------------------------------------------
\section{Research question and sub-questions}
\label{sec:intro-rq}

\noindent\textbf{Main research question.} \\
\textit{How are investment logics constructed, legitimised and contested
within the EIC instruments Pathfinder and STEP, and how can these dynamics
be understood through the lens of institutional theory?}

\medskip
\noindent\textbf{Sub-questions.} The sub-questions are framed to match
the documentary scope of the study: they ask what the Work Programme
text \emph{inscribes}, \emph{constructs} and \emph{prescribes}, rather
than how individual actors enact those prescriptions in practice.
\begin{enumerate}[label=\textbf{SQ\arabic*.},leftmargin=*]
    \item Which institutional logics are inscribed in the Pathfinder and
          STEP texts of the EIC Work Programme 2026, and how are they
          distributed across the instruments' architecture
          (eligibility, evaluation, governance, impact)?
    \item How does the Work Programme construct legitimacy for the
          co-presence of these logics --- through what rhetorical and
          structural devices?
    \item How does STEP reconfigure the relationship between state and
          market logic relative to Pathfinder?
    \item What does the comparison between Pathfinder and STEP reveal
          about the model of public investment the EU is
          institutionalising?
\end{enumerate}

% ----------------------------------------------------------------------------
\section{Theoretical positioning}
\label{sec:intro-theory}
\todoinline{One-paragraph teaser of the theoretical lens. Name the key
constructs the thesis will mobilise (institutional logics, legitimacy,
isomorphism, Scott's three pillars, mission-oriented investment /
developmental state) and signal which are foregrounded.}

% ----------------------------------------------------------------------------
\section{Methodological approach}
\label{sec:intro-method}
\todoinline{Two short paragraphs: documentary qualitative analysis of the
EIC Work Programme 2026, three-pass coding (deductive readthrough,
inductive update, synthesis) through an institutional-theory framework.
Detailed treatment is in Chapter~\ref{ch:methodology}.}

% ----------------------------------------------------------------------------
\section{Scope and delimitations}
\label{sec:intro-scope}
\todoinline{Make explicit what the thesis does \emph{not} cover:
EIC Accelerator and Transition; non-EU innovation policy as
\emph{cases} (DARPA, Temasek and Chinese GGFs appear only as
comparators); quantitative impact evaluation; actor-level enactment
(no interviews). Justify each delimitation briefly.}

% ----------------------------------------------------------------------------
\section{Contributions}
\label{sec:intro-contribution}
\begin{itemize}
    \item \textbf{Theoretical contribution.} \todoinline{Extending
          institutional-logics scholarship into supranational
          public-investment instruments; articulating
          \emph{logic-as-register} (market vocabulary $\neq$ market
          logic) and \emph{tension-dissolution} as analytical
          refinements.}
    \item \textbf{Empirical contribution.} \todoinline{First comparative
          qualitative account of Pathfinder and STEP Scale Up as
          inscribed in the EIC Work Programme 2026.}
    \item \textbf{Practical / policy contribution.} \todoinline{Implications
          for EIC programme design, applicants, and EU policy makers
          --- in particular for FP10 successors to STEP.}
\end{itemize}

% ----------------------------------------------------------------------------
\section{Structure of the thesis}
\label{sec:intro-structure}
The remainder of the thesis is organised as follows.
Chapter~\ref{ch:background} reviews the literature on institutional theory
and on EU innovation funding, situating Pathfinder and STEP within both
streams.
Chapter~\ref{ch:methodology} describes the research design, case selection,
data sources, coding strategy and quality criteria.
Chapter~\ref{ch:results} presents the empirical findings for each instrument
in turn and then comparatively.
Chapter~\ref{ch:discussion} interprets the findings against the theoretical
framework and engages with rival explanations.
Chapter~\ref{ch:conclusion} summarises the contributions, acknowledges
limitations, and proposes avenues for future research.
