%==============================================================================
%  Chapter 3 — Methodology
%
%  Structure:
%   1. Research design & document corpus
%   2. Analytical procedure (three-pass deductive → inductive → synthesis)
%   3. Use of generative AI in the research process
%   4. Quality, reflexivity and limitations
%==============================================================================
\chapter{Methodology}
\label{ch:methodology}

\section*{Chapter overview}

This chapter sets out how the thesis was done. It explains the research
design and the document corpus, the three-pass analytical procedure used
to read that corpus, the way a generative-AI assistant was used in the
workflow, and the quality criteria and limitations that frame what the
study can and cannot claim.

%==============================================================================
\section{Research design \& Document corpus}
\label{sec:meth-corpus}

This thesis takes a qualitative, interpretive approach. It treats policy
text as a primary object of analysis: the EIC Work Programme does not
simply describe the Pathfinder and STEP instruments, it constitutes them
by defining who counts as an applicant, what counts as innovation, and
what counts as success. The analytical task is therefore to read the
text closely and ask what assumptions and commitments it inscribes. This
fits the institutional-theory framework introduced in
Chapter~\ref{ch:background}, which treats categories such as
\enquote{innovation}, \enquote{market} and \enquote{state} as socially
constructed rather than given.

The primary subject of analysis during this thesis have been the EIC
Work Programme 2026, which functions to lay out the priorities and
direction for the different instruments managed by the EIC. The specific
instruments, subject of analysis, are scoped to the Pathfinder and STEP.
\\

The specific instruments, Pathfinder and STEP, were chosen to cover two
crucial inflection points;

\begin{enumerate}[leftmargin=*]
    \item The seed capital (Pathfinder)
    \item The scale-up pre-commercialisation (STEP)
\end{enumerate}

The two instruments sit at opposite ends of the EIC pipeline. Pathfinder
funds early-stage research where the technology is not yet proven; STEP
Scale Up funds companies that already have a working product and need
capital to scale. They share a common institutional home --- the same
agency, the same Work Programme, the same governance structure --- but
they ask for different things from their applicants and reward different
kinds of evidence. That contrast is what makes the comparison useful:
it isolates what changes when the same agency moves from supporting
science to supporting commercialisation. EIC Accelerator and Transition
are deliberately left out of the corpus both to limit the scope and 
because they sit in the middle of the pipeline and would weaken the 
contrast rather than sharpen it.

The corpus consists of a single document: the EIC Work Programme 2026.
The Work Programme implements two legal instruments --- the STEP
Regulation (EU)~2024/795 and the Establishing Horizon Europe
Regulation (EU)~2021/695 --- and cites them as the binding basis for
the rules it sets out. These instruments are not themselves part of
the analysed material; they appear in the thesis only where the Work
Programme cites them, and the citation in those cases is to the Work
Programme. Secondary material such as think-tank commentary, press
coverage and EIC promotional material was also left out. The thesis
asks what the official text inscribes, not how it is received in the
wider field, and that scope follows from the question. The corpus and
the referenced legal instruments are listed in
Appendix~\ref{app:doc-corpus}.

The Work Programme was retrieved as the Commission's officially
published PDF (C(2025)\,7410) and kept locaclly as the canonical
reference. A plain-text working copy was generated to make search and
quoting easier; this is a mechanical step with no interpretive content,
but every passage quoted in Chapter~\ref{ch:results} was checked back
against the original PDF before being used.

The full project tree --- corpus, codebooks, readthrough notes,
synthesis and the LaTeX report --- is held in a Git repository.
Substantive reorganisations are recorded in an append-only audit log
(\texttt{RESTRUCTURE\_LOG.md}). The numbered readthrough entries in
\texttt{Readthrough\_Notes\_v1.md} have stable identifiers, so any
finding reported in Chapter~\ref{ch:results} can be traced back to the
entry it comes from, and from there to the passage in the source PDF.
The chain of custody --- PDF $\rightarrow$ extracted text $\rightarrow$
numbered entry $\rightarrow$ reported finding --- is intentional and
gives the trustworthiness criteria discussed in
Section~\ref{sec:meth-quality} something concrete to point at.

%==============================================================================
\section{Analytical procedure}
\label{sec:meth-analysis}

The analysis ran in three sequential passes. The first applied a set of
framework codebooks deductively to the corpus and produced a numbered
set of coded entries. The second revisited the entries that had been
flagged as ambiguous, resolved them, and developed pattern-level
observations across the corpus. The third synthesised those patterns
into the named findings that Chapter~\ref{ch:results} presents and
Chapter~\ref{ch:discussion} interprets. Each pass fed the next, and the
whole procedure is recorded so any finding can be traced back to the
underlying passages.

\subsection{Pass 1 --- Deductive readthrough}
\label{sec:meth-pass1}

Pass~1 applied two codebooks to the corpus. The first covers Scott's
three pillars and DiMaggio and Powell's three types of isomorphism; the
second covers Thornton, Ocasio and Lounsbury's four institutional logics
(market, state, profession, science). Both codebooks are reproduced in
Appendix~\ref{app:codebook-deductive}.

The output of Pass~1 is a single working document,
\texttt{Readthrough\_Notes\_v1.md}, made up of numbered entries. Each
entry pairs a verbatim passage from the Work Programme with its codings
and a short note explaining the coding. The pass followed a conservative
standard: a logic was coded only where it clearly \emph{organised} the
passage, not merely where its vocabulary was present. This distinction
matters most in the STEP section, where the text uses market vocabulary
heavily but the logic underneath is often state. Passages that did not
fit cleanly were flagged with \texttt{[?]} markers and left for Pass~2
to resolve.

\subsection{Pass 2 --- Inductive update}
\label{sec:meth-pass2}

Pass~2 had two jobs. The first was to work through the \texttt{[?]}
flags from Pass~1 --- re-reading each ambiguous entry against both
codebooks and either resolving it to a coding or, where the ambiguity
was real, recording it as a productive analytical observation. The
second was to look across the resolved entries and develop
pattern-level observations: recurring textual moves that the
entry-by-entry coding could not see on its own
(\textcite{gioia2013seeking} provides the broad data-structure logic).

Inductive codes that emerged in Pass~2 --- categories the deductive
codebooks did not anticipate --- are documented in
Appendix~\ref{app:codebook-inductive}. The resolved flags and the
developed patterns are recorded in the same
\texttt{Readthrough\_Notes\_v1.md} file as Pass~1, so the deductive and
inductive layers sit alongside each other entry by entry.

\subsection{Pass 3 --- Synthesis and writing}
\label{sec:meth-pass3}

Pass~3 produced the cross-entry synthesis (\texttt{synthesis.md}) on
which Chapter~\ref{ch:results} draws. The synthesis tabulates the
logic profile by section of the corpus and organises the findings into
four named patterns: tension-dissolution (Pattern~A), the coercive
governance cluster (Pattern~B), the state social-equity template
(Pattern~C), and the Challenge-chapter logic succession template
(Pattern~D). It also collects a set of STEP-specific dynamics ---
circular market validation, the Sovereignty Seal as a portable
legitimacy device, and mimetic isomorphism against DARPA, Temasek and
Chinese Government Guidance Funds.

Chapter~\ref{ch:discussion} draws on the synthesis rather than
re-reading the corpus, so the entry-level work feeds the chapter-level
interpretation through one mediating document.

%==============================================================================
\section{Use of generative AI in the research process}
\label{sec:meth-genai}

The thesis was written with the systematic support of a generative-AI
(GenAI) assistant.\footnote{Anthropic's \emph{Claude} family of large
language models --- specifically Claude Opus 4.6 and Claude Opus 4.7
--- accessed via the \emph{Claude Code} command-line interface. The
choice between the two versions was determined by the context-window
requirements of the specific task. \todoinline{Insert the period of
use (start--end month/year).}} The
methodological literature on GenAI in qualitative research is still
unsettled, and supervisors and examiners reasonably want to know
exactly how the tool was used. This section sets out the position
taken, the tasks the tool was used for, how the analytical work was
kept anchored to the researcher's own judgement, and the limitations
that follow.

\subsection{Position}
\label{sec:meth-genai-position}

The published literature splits in roughly three directions.
\textcite{zhang2024redefining} and similar work see GenAI as a
productivity extension that, used carefully, can surface themes a
human coder might miss. \textcite{chatzichristos2025qualitative}
warns that the same move risks a quiet return to positivism: treating
coding as a repeatable mechanical operation hands back the reflexive,
interpretive work that defines qualitative analysis.
\textcite{nguyen2025engaged} go further and argue against putting any
AI between the researcher and the empirical material, on the grounds
that meaning is made in the slow work of reading and re-reading.

The position taken here is intermediate. The assistant is treated as
a tool of the researcher --- closer in spirit to qualitative-analysis
software like MAXQDA or NVivo than to a co-analyst --- and not as a
source of analytical judgement. The decisions that anchor the thesis
were made by the researcher: the institutional-theory readings of
Pathfinder and STEP, the identification of patterns such as logic
succession and tension-dissolution, and the framing of TRL as
institutional disguise. The tool was used for the work \emph{around}
those decisions: locating passages, keeping the codebook consistent,
formatting notes, drafting candidate prose for review, and comparing
across entries. Where Nguyen and Welch's warning is sharpest --- handing
pattern identification over to the model --- the workflow was set up so
that the model proposes and the researcher disposes.

\subsection{Tasks the tool was used for}
\label{sec:meth-genai-tasks}

The assistant was used for five categories of task:

\begin{enumerate}[leftmargin=*]
  \item \textbf{Codebook construction.} The deductive codebooks in
        \texttt{04\_codebook/output/} were drafted by the assistant from
        definitions the researcher supplied, then revised against the
        primary literature before being applied.
  \item \textbf{Corpus preparation.} The 188-page Work Programme PDF
        was converted to a plain-text working copy
        (\texttt{03\_corpus/output/WP2026\_extracted.txt}) to support
        search and quoting. No interpretive transformation was
        performed at this step.
  \item \textbf{Pass~1 deductive readthrough.} For each entry, the
        assistant produced a candidate coding against the framework,
        flagged ambiguous passages, and recorded emerging patterns.
        Every entry was reviewed, edited or rejected by the researcher
        before being kept.
  \item \textbf{Cross-entry synthesis.} Once Pass~1 covered enough of
        the corpus, the assistant was asked to identify recurring
        patterns across entries. These were treated as candidate
        observations and tested back against the underlying entries
        before being adopted, refined or dropped.
  \item \textbf{Drafting and editing.} Chapter prose, LaTeX scaffolding
        and bibliography management were drafted with assistance and
        then revised by the researcher. No claim, citation or finding
        appears in the final text without independent verification.
\end{enumerate}

The assistant was explicitly \emph{not} used to: generate or simulate
empirical material; keep coded entries that had not been reviewed by
the researcher; or formulate the thesis' central theoretical argument.

\subsection{Division of labour}
\label{sec:meth-genai-labour}

The workflow was structured around a deliberate division of labour
between researcher and tool. \cref{tab:meth-ai-division} summarises the
allocation.

\begin{table}[ht]
  \centering
  \caption{Division of labour between researcher and GenAI assistant.}
  \label{tab:meth-ai-division}
  \begin{tabular}{p{0.45\linewidth} p{0.45\linewidth}}
    \toprule
    \textbf{Researcher} & \textbf{GenAI assistant} \\
    \midrule
    Research question and theoretical framing & Locating relevant passages in the corpus \\
    Selection of theoretical sources           & Drafting candidate codings against the codebook \\
    Final coding decisions                     & Maintaining schema and formatting consistency \\
    Identification and naming of patterns      & Cross-entry comparison and tabulation \\
    Interpretive argument                      & Drafting prose for researcher review \\
    Citation accuracy and source fidelity      & Bibliography formatting \\
    \bottomrule
  \end{tabular}
\end{table}

The split reflects the position above: the model accelerates work that
is structured, repetitive, or generative-of-candidates; the researcher
keeps every act of judgement on which the validity of the analysis
depends.

\subsection{Audit trail}
\label{sec:meth-genai-audit}

Three practices kept the AI-assisted workflow auditable.

First, the whole project tree is in Git, with the append-only
\texttt{RESTRUCTURE\_LOG.md} recording substantive reorganisations.
The numbered readthrough entries form a chronological record of every
coded passage; their stable numbering means any finding in
Chapter~\ref{ch:results} can be traced back to the entry it derives
from, and from there to the verbatim passage in the source PDF.

Second, candidate codings produced by the assistant were treated as
proposals and reviewed against the codebook. Where a suggestion was
ambiguous or did not fit cleanly, the entry was flagged with a
\texttt{[?]} marker and resolved during Pass~2. The resolved flags are
included as an appendix excerpt (Appendix~\ref{app:audit-trail}).

Third, no quotation, citation or factual claim in this thesis appears
without direct verification against the primary source. The full text
of the Work Programme is held locally and was the canonical reference
at every step. Secondary literature was read in the original rather
than via summary by the assistant. This is the standard mitigation for
the well-documented risk of fabricated citations and factual drift in
large-language-model outputs \parencite{nguyen2025engaged}.

\subsection{Limitations of AI assistance}
\label{sec:meth-genai-limits}

Three limitations are acknowledged.

The first is the \emph{positivist drift} warned about by
\textcite{chatzichristos2025qualitative}. AI-assisted coding can
quietly re-import the assumption that meaning lives in the text and
is recoverable by repeatable procedure. The workflow tries to
mitigate this by keeping all interpretive moves with the researcher
and by working within an institutional-logics framework that is itself
explicit about the social construction of categories. The risk is
reduced, not eliminated.

The second is \emph{anchoring}. Even where the researcher revises a
model-generated coding, the initial suggestion may bias the direction
of attention. Pass~2 was introduced in part to counter this --- by
re-reading entries against unresolved questions rather than against
the original codings.

The third is \emph{opacity}. The model's reasoning is not directly
inspectable and the conditions of its training are only partially
known. For that reason the assistant is treated as a fallible
drafting collaborator whose outputs require verification, not as an
independent source of evidence.

This account is intended to satisfy the responsible-use expectations
that are now common across the qualitative-research community: a
transparent disclosure of GenAI use, a clear statement of researcher
responsibility for the final text, and an explanation of how risks
to integrity and interpretation were managed.

%==============================================================================
\section{Quality, reflexivity and limitations}
\label{sec:meth-quality}

\subsection{Quality criteria}
\label{sec:meth-quality-criteria}

Trustworthiness in this study is addressed through Lincoln and Guba's
four standard criteria for qualitative research: credibility,
transferability, dependability and confirmability.

\emph{Credibility} --- that the analysis stays faithful to what the
text actually says --- was supported in two ways. The numbered entry
format pairs each coding with its verbatim passage, so any coding can
always be checked against its source. As an additional check, the
researcher also worked through the Work Programme by hand on a
printed copy with coloured markers, and that manual coding is
cross-referenced against the digital coding in
\texttt{colour-codes-cross-reference.md}. Where the two passes agreed,
the coding is more confident; where they diverged, the divergence is
documented and explained.

\emph{Transferability} --- that the reader can judge whether the
findings travel to other settings --- is supported by thick
description and verbatim quotation throughout Chapter~\ref{ch:results},
and by an explicit scope statement of where the findings might and
might not apply (Chapter~\ref{ch:discussion}, Boundary conditions).

\emph{Dependability} --- that the analytical procedure is stable and
could in principle be followed by someone else --- rests on the
codebook (Appendix~\ref{app:codebook-deductive}), the audit trail in
\texttt{Readthrough\_Notes\_v1.md}, and the append-only
\texttt{RESTRUCTURE\_LOG.md}. The procedure is documented; the inputs
and outputs of each stage are versioned.

\emph{Confirmability} --- that the findings are grounded in the data
and not in the researcher's prior commitments --- is addressed by the
entry-level coding rationales, the manual cross-reference as an
independent check, and the explicit division of labour with the AI
assistant set out in \cref{sec:meth-genai-labour}.

\subsection{Reflexivity}
\label{sec:meth-reflexivity}

The researcher's background shaped the study and should be stated.
\todoinline{One paragraph: state your DTU affiliation, any prior
exposure to the EIC or to EU innovation policy, and your prior view
of mission-oriented or developmental-state arguments. Be honest about
where that predisposition could have shaped what the study saw or
missed --- and point to where in Chapter~\ref{ch:discussion} the
findings are tested against rival readings.}

\subsection{Ethics}
\label{sec:meth-ethics}

A documentary design on publicly available EU policy texts avoids the
human-subjects ethics concerns that come with interview research. The
only responsible-use question that remains concerns the use of
generative AI, which is addressed in \cref{sec:meth-genai}.

\subsection{Methodological limitations}
\label{sec:meth-limits}

Four methodological limitations are acknowledged here. Substantive
limitations of the findings themselves are kept for
Chapter~\ref{ch:conclusion}.

\begin{enumerate}[leftmargin=*]
  \item \textbf{Single-source scope.} The corpus is a single document.
        The two regulations cited within it were treated as referenced
        legal background, not as coded material. The study sees what
        the Work Programme says, not how it is enacted on the ground.
  \item \textbf{Moving target.} STEP only recently became operational.
        Some of the textual moves analysed here may look different
        once a few funding cycles have run and the instrument has been
        revised.
  \item \textbf{English-language only.} The Work Programme is published
        in English; this study works only from the English text and
        does not compare across language versions.
  \item \textbf{Single-coder design.} The analysis was carried out by
        one researcher. The manual cross-reference described under
        \emph{credibility} is the partial compensation for the absence
        of a second coder; it does not replace inter-rater reliability
        in the strict sense.
\end{enumerate}
