%==============================================================================
%  Chapter 4 — Findings
%
%  Organised around the synthesis (synthesis.md):
%    - logic profile by section (orienting)
%    - four named patterns (A, B, C, D) — each gets its own section
%    - STEP-specific dynamics (state-as-developmental-investor cluster)
%    - TRL as institutional disguise
%    - Sustainability entry mechanisms (addresses programme LO3)
%
%  Keep the chapter descriptive — interpretation belongs in Discussion.
%==============================================================================
\chapter{Findings}
\label{ch:results}

\section*{Chapter overview}
\todoinline{One paragraph: the chapter presents the empirical findings
in the order the synthesis builds them --- a logic profile across the
two instruments, four cross-cutting patterns (A--D), STEP-specific
dynamics, the role of TRL as an institutional device, and the
mechanisms by which sustainability enters the Challenge chapters.}

%==============================================================================
\section{Logic profile by section}
\label{sec:res-profile}
\todoinline{Orienting section. Tabulate the dominant institutional
logic(s) for each section of the corpus (Overview, Pathfinder Open,
Pathfinder Challenges II.2.1--II.2.3, STEP Scale Up access /
eligibility, STEP award criteria). The table reproduces the
\enquote{Logic Profile by Section} table from \texttt{synthesis.md}
\S1 and serves as the navigational frame for the rest of the chapter.
Headline finding to introduce: logic succession across the innovation
pipeline --- as TRL increases, the dominant logic shifts from
\texttt{LOGIC\_SCIENCE} through \texttt{LOGIC\_MARKET} to
\texttt{LOGIC\_STATE}.}

\begin{table}[H]
\centering
\caption[Logic profile by section]{Dominant institutional logics by
section of the EIC Work Programme 2026 (Pathfinder + STEP Scale Up).}
\label{tab:res-profile}
\begin{tabularx}{\textwidth}{@{} l X X @{}}
\toprule
\textbf{Section} & \textbf{Dominant logic(s)} & \textbf{Notes} \\
\midrule
Overview / Introduction          & --- & --- \\
Pathfinder Open --- Key features & --- & --- \\
Pathfinder Open --- Evaluation   & --- & --- \\
Pathfinder Challenges            & --- & --- \\
II.2.1 Advanced Materials        & --- & --- \\
II.2.2 Healthy Ageing            & --- & --- \\
II.2.3 DeepRAP                   & --- & --- \\
STEP --- Access \& eligibility   & --- & --- \\
STEP --- Award criteria          & --- & --- \\
\bottomrule
\end{tabularx}
\end{table}

%==============================================================================
\section{Pattern A --- Tension-dissolution}
\label{sec:res-pattern-a}
\todoinline{Logics are presented as naturally complementary; the text
explicitly dissolves potential conflict by treating logics as
equivalent or mutually reinforcing. Distinguish carefully from
\texttt{LOGIC\_TENSION}, which requires the conflict to be
\emph{surface-visible} in the text. Anchor instances:
[005], [006], [019], [039], [057], [061], [082].}

%==============================================================================
\section{Pattern B --- Coercive governance cluster}
\label{sec:res-pattern-b}
\todoinline{A cluster of passages ([021]--[027], [061]) in which EIC
Programme Managers hold discretionary authority over capital continuity,
roadmap direction, and portfolio placement under legally neutral
grant-mechanics language. Trace the progressive escalation: stated
autonomy ([021]) --- milestone oversight ([023]) --- suspension /
termination authority ([024]) --- soft request to join portfolios
([025]) --- proactive steering ([026]) --- Commission services as
direct participant ([027]) --- dual-responsiveness mandate without
resolution mechanism ([061]).}

%==============================================================================
\section{Pattern C --- State social-equity template}
\label{sec:res-pattern-c}
\todoinline{Near-identical passages embedding gender balance, female
researcher empowerment and underrepresented-groups mandates appear
across multiple instruments and sections with minimal variation
([001], [017], [047], [063], [112], [175]). Argue that the textual
recurrence is itself evidence of standardised state-logic insertion
flowing from EU legislative obligations (Horizon Europe Regulation
gender mainstreaming) rather than instrument-specific commitment.
The tiebreaker paragraph ([059]) confirms structural embedding.}

%==============================================================================
\section{Pattern D --- Challenge-chapter logic succession template}
\label{sec:res-pattern-d}
\todoinline{Each Challenge chapter (II.2.1, II.2.2, II.2.3) follows
the same internal sequence: \texttt{LOGIC\_STATE} (Background \&
Scope) $\rightarrow$ \texttt{LOGIC\_SCIENCE} (Specific Objectives)
$\rightarrow$ \texttt{LOGIC\_PROFESSION} (Portfolio Approach)
$\rightarrow$ \texttt{LOGIC\_STATE} (Expected Impact). Anchor entries:
[095]--[116] and [117]--[129]. Argue that this is template-driven
text architecture, not chapter-specific design.}

%==============================================================================
\section{STEP-specific dynamics}
\label{sec:res-step-dynamics}

\todoinline{Introductory paragraph: STEP exhibits three intertwined
dynamics that together justify reading it as a distinct
state-as-developmental-investor instrument, not as a market-logic
instrument.}

\subsection{State absorbing market vocabulary as legitimation register}
\label{sec:res-step-vocabulary}
\todoinline{Across the STEP section ([130], [132], [139], [146]),
\texttt{LOGIC\_STATE} absorbs and deploys market vocabulary
(\enquote{market gap}, \enquote{Venture Debt}, \enquote{equity},
\enquote{deal flow}) as its own legitimation register --- the
vocabulary signals state-justification-through-market-failure-language,
not market logic governing the passage. Per Rule~15 of the codebook
(vocabulary does not determine logic), each instance was tested
individually. Exceptions where \texttt{LOGIC\_MARKET} is genuinely
operative: Table~9 market-opportunity ([172]), business-model
([173]), and innovation cost/performance ([169]) criteria.}

\subsection{Circular market validation}
\label{sec:res-step-circular}
\todoinline{STEP simultaneously requires demonstrated market interest
(pre-commitment from a qualified investor, 20\% of target round,
[141]) and demonstrated market failure (the amount cannot be fully
financed without EIC, [176]). These are only simultaneously
satisfiable by using EIC's prospective 20--33\% anchor participation
as the lever to obtain the private pre-commitment. The state
constructs the market signal it then requires as proof of market
legitimacy --- consolidating [132], [140], [145], [176].}

\subsection{The Sovereignty Seal as field-bridging legitimacy artefact}
\label{sec:res-step-seal}
\todoinline{The Sovereignty (STEP) Seal: state-issued credential that
travels across institutional fields. Unlocks access to InvestEU
Venture Debt ([152], [161]) and Business Acceleration Services;
crucially, can be awarded even on NO~GO decisions where merit
criteria are met but budget is unavailable ([166]). The decoupling
from the investment decision reveals the Seal as a pure legitimacy
instrument.}

\subsection{Mimetic isomorphism against DARPA, Temasek and Chinese GGFs}
\label{sec:res-step-mimesis}
\todoinline{The Work Programme explicitly benchmarks STEP against US
(DARPA) and Asian (Temasek, Chinese Government Guidance Funds) models.
Document the citation, then characterise the adoption as selective ---
STEP reproduces the equity / catalytic investment mechanics while
embedding them in EU procurement architecture (Funding and Tenders
Portal, quarterly evaluation batches, Commission Award Decision).
The result is a hybrid that does not fully replicate the models it
cites.}

%==============================================================================
\section{TRL as institutional disguise}
\label{sec:res-trl}
\todoinline{The Technology Readiness Level framework presents what
is effectively a regulatory gatekeeping instrument as a scientific
measurement tool. TRL determines eligibility, budget allocation and
instrument routing but is framed as an objective developmental metric
([012], [044], [046]). Borrowed from NASA / US defence contexts, it
carries scientific legitimacy while performing state regulatory work
--- a cognitive-pillar device whose legitimacy effect is precisely
its taken-for-grantedness.}

%==============================================================================
\section{Sustainability entry mechanisms}
\label{sec:res-sustainability}
\todoinline{Testing the flag from [096] across the Challenge chapters
revealed three distinct entry mechanisms for sustainability:
(i)~\textbf{Commission Communication citation} --- sustainability
enters structurally through the cited Communication (RePowerEU, Green
Deal) in II.2.1 [099]; (ii)~\textbf{technical efficiency proxy} ---
compute-constraint requirements in II.2.3 [125], [129] may function
as an indirect environmental mandate in the context of AI data-centre
energy use; (iii)~\textbf{sector definition} --- in STEP, the clean
technology category is defined by sustainability criteria, so
sustainability is the technology category rather than a frame applied
to it ([137]). II.2.3 lacks explicit sustainability language in
Background or Expected Impact, supporting the hypothesis that
sustainability enters through Communications specific to each
Challenge topic, not as a universal insert.}

%==============================================================================
\section{Chapter summary}
\label{sec:res-summary}
\todoinline{One short page summarising the key empirical findings ---
logic succession, the four named patterns, the STEP cluster, TRL,
sustainability mechanisms --- before Chapter~\ref{ch:discussion}
interprets them theoretically.}
