%==============================================================================
%  Chapter 5 — Discussion
%
%  Interpretation against the analytical framework. Each section ties one
%  empirical finding cluster to one theoretical construct and engages with
%  rival explanations. Concludes with theoretical and practical contributions.
%==============================================================================
\chapter{Discussion}
\label{ch:discussion}

\section*{Chapter overview}
\todoinline{State that the chapter (i)~interprets each finding cluster
through the framework constructs in Chapter~\ref{ch:background};
(ii)~engages explicitly with rival explanations; and (iii)~articulates
theoretical and practical contributions.}

%==============================================================================
\section{Logic succession as institutional design}
\label{sec:disc-succession}
\todoinline{Interpret the Science $\rightarrow$ Market $\rightarrow$
State succession (synthesis \S2.1) and Pattern~D as evidence that the
Work Programme architecture is logic-zoned by pipeline position rather
than logic-neutral. Read this through Thornton et al.'s
inter-institutional system: each instrument enacts a different
configuration of the four logics, but the configuration is determined
by where in the pipeline the instrument sits, not by what its
applicants do.}

%==============================================================================
\section{Tension-dissolution as legitimacy work}
\label{sec:disc-tension}
\todoinline{Read Pattern~A through Suchman's legitimacy types.
Presenting competing logics as complementary is a \emph{cognitive
legitimacy} move: it performs institutional coherence rather than
arguing for it. The absence of acknowledged conflict is not
neutrality --- it is rhetorical work. Connect to the broader
hybridisation literature on how institutions absorb contradiction.}

%==============================================================================
\section{Coercive governance under an autonomy register}
\label{sec:disc-coercive}
\todoinline{Read Pattern~B through Scott's regulative pillar and
DiMaggio \& Powell's coercive isomorphism. The EIC formally protects
researcher autonomy ([021]) while retaining hard override authority
over capital continuity through the Programme Manager. The gap
between the stated autonomy principle and the operative control
structure is the central interpretive puzzle. Engage with the
alternative reading --- that Pattern~B is \texttt{LOGIC\_STATE}
operating through professional instruments rather than a distinct
administrative-managerial logic --- and state your position.}

%==============================================================================
\section{TRL as institutional disguise}
\label{sec:disc-trl}
\todoinline{Read TRL through Scott's cognitive pillar. The framework
presents regulatory gatekeeping as scientific measurement, borrowing
NASA / US-defence legitimacy. The political question of where in the
pipeline public money flows is reframed as a technical question of
developmental readiness --- a cognitive-pillar move whose efficacy
depends on TRL's taken-for-grantedness in the innovation policy field.}

%==============================================================================
\section{STEP as a developmental-state instrument}
\label{sec:disc-step}

\todoinline{Introductory paragraph: STEP is best read not as the EU
adopting market-VC logic but as a developmental-state instrument
deploying market mechanics. The three sub-sections develop this in
turn.}

\subsection{Circular market validation}
\label{sec:disc-step-circular}
\todoinline{The simultaneous requirements of demonstrated market
interest and demonstrated market failure are only satisfiable through
EIC's own anchor participation. Read against Mazzucato's
entrepreneurial / patient capital model and the Chinese Government
Guidance Fund literature: the state \emph{constructs} the market
signal it then requires. Whether this is a fundamental contradiction
or a deliberate developmental-state design choice is the central
theoretical question of the STEP analysis; argue for the latter.}

\subsection{The Sovereignty Seal as field-bridging legitimacy}
\label{sec:disc-step-seal}
\todoinline{Read the Sovereignty Seal through Suchman: a pragmatic
legitimacy device (gives access to InvestEU resources) carrying moral
legitimacy undertones (strategic alignment with EU interests). The
decoupling from the investment decision ([166]) reveals the Seal as
a pure legitimacy instrument that travels across public and private
fields. Discuss as an institutional innovation worth naming.}

\subsection{Mimetic isomorphism vs DARPA, Temasek and Chinese GGFs}
\label{sec:disc-step-mimesis}
\todoinline{The explicit benchmarking against DARPA, Temasek and
Chinese Government Guidance Funds is mimetic isomorphism at the
instrument-design level. Discuss what STEP reproduces (equity /
catalytic mechanics; state anchor position) and what it does not
(operational autonomy from the political principal; mission focus
defined by the agency). The hybrid that results sits closer to the
Chinese GGF model than to DARPA --- worth saying explicitly.}

%==============================================================================
\section{Rival explanations}
\label{sec:disc-rival}
\todoinline{Engage with three rival readings: (i)~a
\textbf{Varieties-of-Capitalism / liberal-market} read --- STEP is
straightforward state aid in market vocabulary, no developmental
inflection; (ii)~a \textbf{realpolitik strategic-autonomy} read ---
the logic is geopolitics, not institutional theory; (iii)~a
\textbf{path-dependence / budget-cycle} read --- STEP is the
predictable next move in an EU funding cycle. Argue why the
institutional reading adds explanatory value over each.}

%==============================================================================
\section{Theoretical contributions}
\label{sec:disc-contrib}
\begin{enumerate}
    \item \todoinline{Extension of the institutional-logics literature
          to supranational public-investment instruments, with the
          \emph{logic-as-register} distinction
          (market vocabulary $\neq$ market logic) as the main
          analytical refinement.}
    \item \todoinline{Articulation of \emph{tension-dissolution} as a
          distinct legitimacy strategy adjacent to but distinct from
          surface-visible logic conflict.}
    \item \todoinline{The \emph{Sovereignty Seal} as an empirical
          example of a portable, field-bridging legitimacy artefact ---
          an institutional device worth naming.}
    \item \todoinline{\emph{Circular market validation} as a
          characteristic of developmental-state investment design,
          with STEP as the EU instance.}
\end{enumerate}

%==============================================================================
\section{Practical and policy implications}
\label{sec:disc-practice}

\subsection{For EIC programme design}
\label{sec:disc-prog-eic}
\todoinline{What the EIC should make explicit (the developmental-state
character of STEP; the directive authority of Programme Managers; the
role of the Seal). What the trade-offs are.}

\subsection{For applicants and intermediaries}
\label{sec:disc-prog-app}
\todoinline{How applicants should read each instrument's investment
logic: what the evaluation is actually selecting for. The role of the
Seal as a legitimacy credential independently of the funding decision.}

\subsection{For EU policy makers}
\label{sec:disc-prog-eu}
\todoinline{Implications for the design of mission-driven funding
instruments in FP10 and successors. Whether the developmental-state
inflection is a one-off or a template.}

%==============================================================================
\section{Boundary conditions}
\label{sec:disc-boundary}
\todoinline{Where do the findings travel? --- other EU instruments
with similar architectures (Innovation Fund, EU Sovereignty Fund if
established). Where do they not? --- mission-oriented instruments in
liberal-market national systems may behave differently. Be explicit
about scope.}
