%==============================================================================
%  Chapter 5 — Discussion
%
%  This is where interpretation happens. Discuss the findings against the
%  framework, engage rival explanations, draw out theoretical and practical
%  contributions.
%==============================================================================
\chapter{Discussion}
\label{ch:discussion}

\section*{Chapter overview}
\todoinline{State that the chapter (i) interprets the findings against the
framework, (ii) discusses rival explanations, (iii) develops theoretical and
practical contributions.}

%==============================================================================
\section{Interpreting investment logics through institutional theory}
\label{sec:disc-interpretation}

\subsection{Pathfinder as a science-led exploration logic}
\label{sec:disc-pf}
\todoinline{Tie the Pathfinder logic back to specific institutional-theory
constructs (e.g.\ profession logic, normative legitimacy).}

\subsection{STEP as a strategic-autonomy market-shaping logic}
\label{sec:disc-step}
\todoinline{Tie the STEP logic back to other constructs (e.g.\ state logic,
coercive isomorphism, mission-orientation).}

\subsection{Co-existence and hybridisation}
\label{sec:disc-hybrid}
\todoinline{How do the two logics co-exist inside the same institutional
home? What hybridisation mechanisms emerge?}

%==============================================================================
\section{Rival explanations}
\label{sec:disc-rival}
\todoinline{Engage seriously with at least two alternatives — e.g.\ a pure
political-economy account, a resource-dependence account, a
budget-cycle/path-dependence account — and explain why the institutional
reading still adds value.}

%==============================================================================
\section{Theoretical contributions}
\label{sec:disc-theory}
\begin{enumerate}
    \item \todoinline{Specify how the thesis extends the
          institutional-logics literature into supranational innovation
          policy.}
    \item \todoinline{Specify the new empirical phenomena it brings to
          light (e.g.\ the STEP Seal as a hybridisation device).}
    \item \todoinline{Specify any conceptual refinements (e.g.\ the
          construct of an \emph{instrument-level investment logic}).}
\end{enumerate}

%==============================================================================
\section{Practical and policy implications}
\label{sec:disc-practice}

\subsection{For EIC programme design}
\todoinline{What should the EIC do differently?}

\subsection{For applicants and intermediaries}
\todoinline{How should applicants read the two instruments?}

\subsection{For EU policy makers}
\todoinline{Implications for the design of mission-driven funding instruments
in the next Framework Programme (FP10).}

%==============================================================================
\section{Boundary conditions}
\label{sec:disc-boundary}
\todoinline{Where do the findings travel? Where do they not? Be explicit
about scope.}
