%==============================================================================
%  Appendix
%  Each appendix becomes a "chapter" under the \appendix block in main.tex
%  (so they appear as Appendix A, B, C, ...).
%==============================================================================

\chapter{Interview guide}
\label{app:interview-guide}

\section*{Introduction read to the informant}
\todoinline{Standard preamble explaining the project, anonymity, recording
consent and right to withdraw.}

\section*{Core questions}
\begin{enumerate}
    \item Could you describe your role in relation to
          \todoinline{Pathfinder / STEP}?
    \item How would you describe the goals this instrument is trying to
          achieve?
    \item What does a \enquote{good} investment look like in this
          instrument?
    \item Where do you see tensions or trade-offs in the selection process?
    \item How does this instrument compare with others you have worked
          with?
    \item Is there anything important I have not asked about?
\end{enumerate}

%==============================================================================
\chapter{Document corpus}
\label{app:doc-corpus}

\todoinline{Tabulate the documents analysed. Include identifier, title,
issuer, date, type, source.}

\begin{longtable}{@{} l p{6.5cm} l l l @{}}
\toprule
\textbf{ID} & \textbf{Title} & \textbf{Issuer} & \textbf{Year} & \textbf{Type} \\
\midrule
\endfirsthead
\toprule
\textbf{ID} & \textbf{Title} & \textbf{Issuer} & \textbf{Year} & \textbf{Type} \\
\midrule
\endhead
\bottomrule
\endfoot
D01 & EIC Work Programme 2024 & European Commission & 2024 & Policy doc \\
D02 & STEP Regulation (EU) 2024/795 & European Parliament \& Council & 2024 & Regulation \\
D03 & --- & --- & --- & --- \\
\end{longtable}

%==============================================================================
\chapter{Coding scheme}
\label{app:coding}

\todoinline{Final codebook: first-order codes, second-order themes,
aggregate dimensions. A figure of the Gioia data structure works very well
here.}

%==============================================================================
\chapter{Consent form (template)}
\label{app:consent}

\todoinline{Paste the GDPR-compliant consent form used during fieldwork.}

%==============================================================================
\chapter{Supplementary tables and figures}
\label{app:supplementary}

\todoinline{Anything that did not fit in the main text but supports the
argument.}
