%==============================================================================
%  Appendix
%  Each appendix becomes a "chapter" under the \appendix block in main.tex
%  (so they appear as Appendix A, B, C, ...).
%
%  This thesis uses a documentary design (no interviews), so the appendices
%  document the corpus, the codebooks and supplementary analytical material.
%==============================================================================

\chapter{Document corpus}
\label{app:doc-corpus}

\section*{Analysed corpus}

The corpus consists of a single document, listed below. Every coded
passage in \texttt{Readthrough\_Notes\_v1.md} is drawn from this
document.

\begin{longtable}{@{} l p{6.5cm} l l l @{}}
\toprule
\textbf{ID} & \textbf{Title} & \textbf{Issuer} & \textbf{Year} & \textbf{Type} \\
\midrule
\endfirsthead
\toprule
\textbf{ID} & \textbf{Title} & \textbf{Issuer} & \textbf{Year} & \textbf{Type} \\
\midrule
\endhead
\bottomrule
\endfoot
D01 & EIC Work Programme 2026 (Pathfinder \& STEP Scale Up sections, C(2025) 7410) & European Commission & 2026 & Policy doc \\
\end{longtable}

\section*{Legal instruments referenced within the corpus}

The two regulations below are cited by the Work Programme as the
binding legal basis for the rules it implements. They are listed here
for reference only --- they were not themselves coded or analysed, and
they appear in the thesis only where the Work Programme cites them.

\begin{longtable}{@{} l p{6.5cm} l l l @{}}
\toprule
\textbf{ID} & \textbf{Title} & \textbf{Issuer} & \textbf{Year} & \textbf{Type} \\
\midrule
\endfirsthead
\toprule
\textbf{ID} & \textbf{Title} & \textbf{Issuer} & \textbf{Year} & \textbf{Type} \\
\midrule
\endhead
\bottomrule
\endfoot
R01 & STEP Regulation (EU) 2024/795 & European Parliament \& Council & 2024 & Regulation \\
R02 & Establishing Horizon Europe --- Regulation (EU) 2021/695 & European Parliament \& Council & 2021 & Regulation \\
\end{longtable}

%==============================================================================
\chapter{Deductive codebook}
\label{app:codebook-deductive}

\todoinline{Reproduce (or summarise) the deductive codebook used in
Pass~1 of the analysis: Scott's three pillars, DiMaggio \& Powell's
isomorphism types, and Thornton et al.'s institutional logics. Provide
code definition, example indicators, and source.}

%==============================================================================
\chapter{Inductive codes and pattern-level observations}
\label{app:codebook-inductive}

\todoinline{Document the inductive codes that emerged in Pass~2 to
resolve \texttt{[?]} flags, together with the pattern-level observations
(Gioia-style data structure works well here).}

%==============================================================================
\chapter{Readthrough audit trail (excerpt)}
\label{app:audit-trail}

\todoinline{Include a representative excerpt from
\texttt{Readthrough\_Notes\_v1.md} showing how passages were coded —
this evidences dependability and confirmability.}

